Title of submission to PLOS journal

### 2019-08-23 docs/manuscript_draft.Rmd
new figs

## WGCNA characterization

This first image was made using [`08_WGCNA_1.R`](https://github.com/macmanes-lab/DoveParentsRNAseq/blob/master/analysis/08_WGCNA_1.R), which was modified from the [first in a series of WGCNA tutorial](https://horvath.genetics.ucla.edu/html/CoexpressionNetwork/Rpackages/WGCNA/Tutorials/Consensus-DataInput.R). The first tutorial focuses on data input, cleaning and pre-processing; outlier removal; clustering of samples by their Euclidean distance; a comparison of sample cluster to sample meta data.

```{r wgcna, message=FALSE, warning=FALSE, cache=TRUE, echo = F, fig.width= 5}
source("../analysis/08_WGCNA_1.R")

>>>>

# Figures

```{r wgcna, message=FALSE, warning=FALSE, cache=TRUE, echo = F, fig.width= 5}
source("../analysis/08_WGCNA_1.R")
subsetWGCNA(whichgroups = c("female.gonad", "female.hypothalamus", "female.pituitary",
                           "male.gonad", "male.hypothalamus", "male.pituitary"),
            mytitle = "Characterization dendrogram with trait heatmap")
```

**Fig 1. Characterization dendrogram with trait heatmap.**.
Most hypothalamus and pituitary samples separte form the gonad samples, but some are clusters contain samples from all tissues.The top panel is a dendrogram showing Euclidean distance of sample. Females (white), males (red), gonad (white), hypothalamus (pink), pituitary (red).

```{r wgcna-female, message=FALSE, warning=FALSE, cache=TRUE, echo = F, fig.width= 5}
subsetWGCNA(whichgroups = c("female.gonad", "female.hypothalamus", "female.pituitary"),
            mytitle = "Female sample dendrogram with trait heatmap")
```

**Fig 2. Female characterization dendrogram with trait heatmap.**. 
Most pituitary samples form a single cluster. More hypothalamus samples cluster with gonads than with pituitary. The top panel is a dendrogram showing Euclidean distance of sample. Females (white), males (red), gonad (white), hypothalamus (pink), pituitary (red).

```{r wgcna-male, message=FALSE, warning=FALSE, cache=TRUE, echo = F, fig.width= 5}
subsetWGCNA(c("male.gonad", "male.hypothalamus", "male.pituitary"),
            mytitle = "Male sample dendrogram with trait heatmap")
```

**Fig 3. Male characterization dendrogram with trait heatmap.**. 
 As with females, most pituitary samples form a single cluster, while more hypothalamus samples cluster with gonads than with pituitary.

### 2019-08-23 docs/manuscript_draft.tex
new figs

>>>>

\hypertarget{figures}{%
\section{Figures}\label{figures}}

\includegraphics{manuscript_draft_files/figure-latex/wgcna-1.pdf}

\textbf{Fig 1. Characterization dendrogram with trait heatmap.}. Most
hypothalamus and pituitary samples separte form the gonad samples, but
some are clusters contain samples from all tissues.The top panel is a
dendrogram showing Euclidean distance of sample. Females (white), males
(red), gonad (white), hypothalamus (pink), pituitary (red).

\includegraphics{manuscript_draft_files/figure-latex/wgcna-female-1.pdf}

\textbf{Fig 2. Female characterization dendrogram with trait heatmap.}.
Most pituitary samples form a single cluster. More hypothalamus samples
cluster with gonads than with pituitary. The top panel is a dendrogram
showing Euclidean distance of sample. Females (white), males (red),
gonad (white), hypothalamus (pink), pituitary (red).

\includegraphics{manuscript_draft_files/figure-latex/wgcna-male-1.pdf}

\textbf{Fig 3. Male characterization dendrogram with trait heatmap.}. As
with females, most pituitary samples form a single cluster, while more
hypothalamus samples cluster with gonads than with pituitary.
